Weighted Model Counting with Conditional Weights for Bayesian Networks

### 2021-02-10 doc/paper2/paper.tex
Rewrite the experiments section

\citet{DBLP:conf/aaai/SangBK05} claim that
\texttt{sbk05} is a smaller encoding than \texttt{d02} with respect to both the
number of clauses and the number of variables but provide no experimental
comparison. \citet{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with
\texttt{d02} by measuring the time it takes to compile either encoding into an
arithmetic circuit. They show that
\texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
(as measured by the number of edges). In their subsequent paper, the same
authors perform two sets of experiments (that are relevant to this summary)
\citep{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
\texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
normal form \citep{DBLP:journals/jancl/Darwiche01}), measuring both compilation
time and numbers of edges in the d-DNNF diagram. The results are mostly in
favour of \texttt{cd06}. Second, they compare the inference time of
\texttt{sbk05} run with \textsf{Cachet} \citep{DBLP:conf/sat/SangBBKP04} with
the compile times of \texttt{cd05} and \texttt{cd06}, but only on five (types
of) instances. In these experiments, \texttt{cd06} is always faster than
\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
slightly slower. The performance difference between \texttt{sbk05} and
\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
five instances and worse on the remaining two. Finally,
\citet{DBLP:conf/ecai/BartKLM16} introduce \texttt{bklm16} and show that it has
both fewer variables and fewer clauses than \texttt{cd06}. Their experiments
show \texttt{bklm16} to be superior to \texttt{cd06} with respect to both
compilation time and encoding size when both are compiled using \textsf{c2d}
\citep{DBLP:conf/ecai/Darwiche04} but inferior to \texttt{cd06} when
\texttt{cd06} is compiled using
\textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} (which still uses
\textsf{c2d} but considers the structure of the Bayesian network along with its
encoding).

Our experiments in \cref{sec:experiments} compare the five previous encodings
along with a newly proposed one---with originally-proposed WMC algorithms as
well as with \textsf{ADDMC}---with respect to the total time it takes to encode
a Bayesian network, compile it or run a WMC algorithm on it, and extract the
(numerical) answer. We confirm some of the findings outlined in this section
while also observing that the (relative and absolute) performance of each
encoding depends on the WMC algorithm in use, and smaller encodings are not
necessarily faster.

@@

\subsection{The Space of Functions on Boolean Algebras}
% TODO: properly define what logical operations on ADDs do. Mistake in the
% paper: an ADD is just a pseudo-boolean function: All operations on ADDs
% (whatever they are) are pointwise (perhaps /\, \/, ~ may be exceptions).

We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
can be efficiently represented using ADDs. Furthermore, all of the operations
are supported by the CUDD \citep{somenzi1998cudd} package that is used by
\textsf{ADDMC} for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The
definitions of multiplication and projection are as defined by
\citet{DBLP:conf/aaai/DudekPV20}, while others are new.

@@

Note that if $U$ is any set, then $\mathcal{V} = \{ \alpha\colon 2^X \to
\mathbb{R}_{\ge 0} \mid X \subseteq U \}$ is a semi-vector space with three
additional operations: (non-scalar) multiplication, complement, and projection.
Specifically, note that both addition and multiplication are both associative
and commutative.

We end the discussion on function spaces by defining several special functions:
unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $1(\emptyset) = 1$,
zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$ defined as $0(\emptyset) = 0$,
and function $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as
$[a](\emptyset) = 0$, $[a](\{a\}) = 1$ for any $a$. Henceforth, for any function
$\alpha\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set $T$, we will write
$\alpha(T)$ to mean $\alpha(T \cap X)$.

@@

\section{Experimental Comparison} \label{sec:experiments}
% TODO: introduce \textsf{query-dnnf}
% \footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} (also
% talk more about how Cachet and Ace are used)
% TODO: included original WMC algorithms
% TODO: Even instances that are solved in less than 0.1 s are too big for edge
% count to be efficiently calculated.
% TODO: my plot's sbk05 data should match (and matches) the ADDMC/DPMC vs c2d
% comparison in the paper (although my sbk05 data only roughly corresponds to
% half of their dataset)
% TODO: mention that both encoding and inference times are limited to 1000 s
% TODO: mention that we don't run ADDMC+cd05 and ADDMC+cd06 because they don't produce correct answers
% TODO: the -implicit flag is disabled for good reasons for bklm16
% TODO: potential appendix: exact arguments to each piece of software

@@

\begin{table}
  \centering
  \caption{The numbers of instances (out of 1466) solved by
    each combination of algorithm and encoding (uniquely, faster than others, and in total).}%
  \begin{tabular}{lrrr}
    \toprule
    Algorithm \& Encoding & Unique & Fastest & Total \\
    \midrule
    $\textsf{Ace} + \texttt{cd05}$ & \textcolor{gray}{0} & 55 & 1169 \\
    $\textsf{Ace} + \texttt{cd06}$ & \textbf{34} & 218 & \textbf{1259} \\
    $\textsf{Ace} + \texttt{d02}$ & \textcolor{gray}{0} & 46 & 993 \\
    $\textsf{ADDMC} + \texttt{bklm16}$ & \textcolor{gray}{0} & 29 & \textcolor{gray}{617} \\
    $\textsf{ADDMC} + \texttt{cw}$ & 14 & \textbf{770} & 919 \\
    $\textsf{ADDMC} + \texttt{d02}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 703 \\
    $\textsf{ADDMC} + \texttt{sbk05}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 729 \\
    $\textsf{Cachet} + \texttt{sbk05}$ & 13 & 229 & 928 \\
    $\textsf{query-dnnf} + \texttt{bklm16}$ & \textcolor{gray}{0} & 3 & 1017 \\
    \bottomrule
  \end{tabular}
  \label{tbl:tallies}
\end{table}

@@

In this section, we describe an experimental study comparing the five WMC
encodings for Bayesian networks when run with \textsf{ADDMC}. The experiments
were run on servers with Intel Xeon Gold 6138 and Intel Xeon E5-2630
processors\footnote{Each instance is run on the same processor for all
  encodings.} running Scientific~Linux~7 with a \SI{32}{\gibi\byte} memory limit
and a \SI{1000}{\second} timeout.

@@

For all encodings other than \texttt{cw}, we use their implementation in
\textsf{Ace}~3.0 with
\texttt{-encodeOnly} and \texttt{-noEclause} flags. However, \textsf{Ace} was
not used to encode evidence, as preliminary experiments revealed that the
evidence-encoding implementation contains bugs that can lead to incorrect
answers or a Java exception being thrown on some instances of the data set (and
the source code is not publicly available). Instead, we simply list all the
evidence as additional clauses in the encoding.

Note that both \texttt{cd05} and \texttt{cd06} purposefully produce overly
relaxed encodings that contain extra models and thus yield incorrect
probabilities \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}. These
additional models are supposed to be filtered out during circuit compilation
\citep{DBLP:conf/ijcai/ChaviraD05}, but this is not easily achievable with
\textsf{ADDMC}. Nonetheless, we include both encodings in the experiments.

While encoding time itself was not measured because of different languages of
implementation, it is worth noting that \texttt{cw} is linear in the total
number of CPT rows and so is unlikely to be slower than, e.g., \texttt{cd06},
which relies on solving $\NP{}$-complete problems as part of the encoding process
\citep{DBLP:conf/sat/ChaviraD06}.

For experimental data, we use the Bayesian networks available with \textsf{Ace}
and
\textsf{Cachet}\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}},
most of which happen to be binary. We classify them into the following seven
categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
\item Mastermind, and
\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \citep{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
  \citep{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}
We run \textsf{ADDMC} with each of the five encodings once on each Bayesian
network.

According to the cumulative plot in \cref{fig:cumulative}, \texttt{cw} is
consistently able to solve more instances with any given time limit than any
other encoding, while the order of the remaining encodings from best to worst is
exactly the opposite of that in previous literature (cf. \cref{sec:related}).
Specifically, \texttt{cw} solves the same number of instances in
\SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second}, which is the
second-best encoding in our experiments. Furthermore, \cref{tbl:tallies} shows
that \texttt{cw} was the fastest in 935 out of the 980 (i.e.,
\SI{95.4}{\percent}) instances that it managed to solve. Finally, according to
the scatter plots in \cref{fig:scatter}, \texttt{cw} is particularly promising
on Grid networks while losing to \texttt{d02} on some instances of the
Mastermind data set. We conjecture that this is so either because the particular
structure of the problem confuses the heuristics used by \textsf{ADDMC} or
because these instances allow for significant simplifications that are exploited
by \texttt{d02} but not \texttt{cw}.

@@

\paragraph{Explaining the performance benefits.} Let $n = |\mathcal{V}|$ be the
number of vertices in the Bayesian network, $d = \max_{X \in \mathcal{V}}
|\mathrm{pa}(X)|$ the maximum in-degree (i.e., the number of parents), and $v =
\max_{X \in \mathcal{V}} |\im X|$ the maximum number of values per variable.
\Cref{tbl:asymptotes} shows how \texttt{cw} has fewer variables and fewer
ADDs than any other encoding. However, note that these are upper bounds and most
encodings (including \texttt{cw}) can be smaller in certain situations (e.g.,
with binary random variables or when a CPT has repeating probabilities). We
equate clauses and ADDs (more specifically, factors of the function $\phi$ from
\cref{alg:encoding}) here because \textsf{ADDMC} interprets each clause of any
WMC encoding as a multiplicative factor of the ADD that represents the entire
WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For literal-weight encodings,
each weight is also a factor, but that does not affect the asymptotic bounds in
the table.

@@

\end{document}

>>>>

\citet{DBLP:conf/aaai/SangBK05} claim that
\texttt{sbk05} is a smaller encoding than \texttt{d02} with respect to both the
number of clauses and the number of variables but provide no experimental
comparison. \citet{DBLP:conf/ijcai/ChaviraD05} compare \texttt{cd05} with
\texttt{d02} by measuring the time it takes to compile either encoding into an
arithmetic circuit. They show that
\texttt{cd05} always compiles faster and results in a smaller arithmetic circuit
(as measured by the number of edges). In their subsequent paper, the same
authors perform two sets of experiments (that are relevant to this summary)
\citep{DBLP:conf/sat/ChaviraD06}. First, they compile \texttt{cd05} and
\texttt{cd06} encodings into d-DNNF (i.e., deterministic decomposable negation
normal form \citep{DBLP:journals/jancl/Darwiche01}), measuring both compilation
time and numbers of edges in the d-DNNF diagram. The results are mostly in
favour of \texttt{cd06}. Second, they compare the inference time of
\texttt{sbk05} run with \textsf{Cachet} \citep{DBLP:conf/sat/SangBBKP04} with
the compile times of \texttt{cd05} and \texttt{cd06}, but only on five (types
of) instances. In these experiments, \texttt{cd06} is always faster than
\texttt{cd05}, while the comparison with \texttt{sbk05} is mixed. Sometimes
\texttt{cd06} is orders of magnitude faster than \texttt{sbk05}, sometimes
slightly slower. The performance difference between \texttt{sbk05} and
\texttt{cd05} is even harder to judge: \texttt{sbk05} is better on three out of
five instances and worse on the remaining two. Finally,
\citet{DBLP:conf/ecai/BartKLM16} introduce \texttt{bklm16} and show that it has
both fewer variables and fewer clauses than \texttt{cd06}. Their experiments
show \texttt{bklm16} to be superior to \texttt{cd06} with respect to both
compilation time and encoding size when both are compiled using
\textsf{c2d}\footnote{\url{http://reasoning.cs.ucla.edu/c2d/}}
\citep{DBLP:conf/ecai/Darwiche04} but inferior to \texttt{cd06} when
\texttt{cd06} is compiled using
\textsf{Ace}\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} (which still uses
\textsf{c2d} but considers the structure of the Bayesian network along with its
encoding). Our experiments in \cref{sec:experiments} confirm some of the
findings outlined in this section while also observing that the (relative and
absolute) performance of each encoding depends on the WMC algorithm in use, and
smaller encodings are not necessarily faster.

@@

\subsection{The Space of Functions on Boolean Algebras}
% TODO: it would be easier to talk about pseudo-Boolean functions instead, but
% maybe it's not necessary.

We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
can be efficiently represented using ADDs. Furthermore, all of the operations
are supported by CUDD \citep{somenzi1998cudd}---a package used by \textsf{ADDMC}
for ADD manipulation \citep{DBLP:conf/aaai/DudekPV20}. The definitions of
multiplication and projection are as defined by
\citet{DBLP:conf/aaai/DudekPV20}, while others are new.

@@

In summary, addition, multiplication, and scalar multiplication are defined
pointwise, while complement and projection interact with the algebraic structure
of the domains $2^X$ and $2^Y$. Specifically, note that both addition and
multiplication are both associative and commutative. We end the discussion on
function spaces by defining several special functions: unit $1\colon 2^\emptyset
\to \mathbb{R}_{\ge 0}$ defined as $1(\emptyset) = 1$, zero $0\colon 2^\emptyset
\to \mathbb{R}_{\ge 0}$ defined as $0(\emptyset) = 0$, and function $[a]\colon
2^{\{a\}} \to \mathbb{R}_{\ge 0}$ defined as $[a](\emptyset) = 0$, $[a](\{a\}) =
1$ for any $a$. Henceforth, for any function $\alpha\colon 2^X \to
\mathbb{R}_{\ge 0}$ and any set $T$, we will write $\alpha(T)$ to mean $\alpha(T
\cap X)$.

@@

\section{Experimental Comparison} \label{sec:experiments}

@@

\begin{table}
  \centering
  \caption{The numbers of instances (out of 1466) solved by
    each combination of algorithm and encoding (uniquely, faster than others, and in total).}%
  \begin{tabular}{lrrr}
    \toprule
    Algorithm \& Encoding & Unique & Fastest & Total \\
    \midrule
    $\textsf{Ace} + \texttt{cd05}$ & \textcolor{gray}{0} & 55 & 1169 \\
    $\textsf{Ace} + \texttt{cd06}$ & \textbf{34} & 218 & \textbf{1259} \\
    $\textsf{Ace} + \texttt{d02}$ & \textcolor{gray}{0} & 46 & 993 \\
    $\textsf{ADDMC} + \texttt{bklm16}$ & \textcolor{gray}{0} & 29 & \textcolor{gray}{617} \\
    $\textsf{ADDMC} + \texttt{cw}$ & 14 & \textbf{770} & 919 \\
    $\textsf{ADDMC} + \texttt{d02}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 703 \\
    $\textsf{ADDMC} + \texttt{sbk05}$ & \textcolor{gray}{0} & \textcolor{gray}{0} & 729 \\
    $\textsf{c2d} + \texttt{bklm16}$ & \textcolor{gray}{0} & 3 & 1017 \\
    $\textsf{Cachet} + \texttt{sbk05}$ & 13 & 229 & 928 \\
    \bottomrule
  \end{tabular}
  \label{tbl:tallies}
\end{table}

@@

% TODO: keep mentioning citations along with algorithm and encoding names

In this section, we describe an experimental study comparing the six WMC
encodings for Bayesian networks when run with both \textsf{ADDMC} and the
WMC algorithms used in the original papers.\footnote{Both
  \texttt{cd05} and \texttt{cd06} cannot be run with most WMC algorithms
  including \textsf{ADDMC} because these encodings allow for additional models
  that the WMC algorithm is supposed to ignore
  \citep{DBLP:conf/ijcai/ChaviraD05,DBLP:conf/sat/ChaviraD06}.} We compare the
encodings with respect to the total time it takes to encode a Bayesian network,
compile it or run a WMC algorithm on it, and extract the (numerical) answer.
Note that while all five papers that introduce other encodings include
experimental comparisons of encoding size, that is not feasible with
\textsf{ADDMC} as even instances that are fully solved in less than
\SI{0.1}{\second} are too big to build the full ADD within reasonable time and
memory limits. The experiments were run on a computing cluster with Intel Xeon
Gold 6138 and Intel Xeon E5-2630 processors\footnote{Each instance is run on the
  same processor for all encodings.} running Scientific~Linux~7 with a
\SI{32}{\gibi\byte} memory limit and a \SI{1000}{\second} timeout on both
encoding and inference. For inference, we use \textsf{Ace} for \texttt{cd05},
\texttt{cd06}, and \texttt{d02};
\textsf{Cachet}\footnote{\url{https://cs.rochester.edu/u/kautz/Cachet/}}
\citep{DBLP:conf/sat/SangBBKP04} for \texttt{sbk05}; and \textsf{c2d}
\citep{DBLP:conf/ecai/Darwiche04} for compilation and \textsf{query-dnnf}
\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}} for
answer computation for \texttt{bklm16}. For encoding, we use \textsf{bn2cnf}
\footnote{\url{http://www.cril.univ-artois.fr/KC/bn2cnf.html}} for
\texttt{bklm16}, and \textsf{Ace} for all other encodings (except for
\texttt{cw}, which is implemented in Python).

\paragraph{Workarounds.} \textsf{Ace} was not used to encode evidence, as
preliminary experiments revealed that the evidence-encoding implementation
contains bugs that can lead to incorrect answers or a Java exception being
thrown on some instances of the data set (and the source code is not publicly
available). Instead, we simply list all the evidence as additional clauses in
the encoding. Furthermore, to ensure that \texttt{bklm16} (whether run with
\textsf{ADDMC} or \textsf{c2d}) returns correct answers on most instances, we
had to disable one of the improvements that \texttt{bklm16} brings over
\texttt{cd06}, namely, the construction of a scaling factor that `absorbs' one
probability from each CDT \citep{DBLP:conf/ecai/BartKLM16}. For realistic
benchmark instances, this scaling factor can easily be below $10^{-30}$, and
thus would require arbitrary-precision floating-point arithmetic to be usable.
Even a toy Bayesian network with seven binary independent variables with
probabilities $0.1$ and $0.9$ is enough for \textsf{bn2cnf} to output precisely
zero as the scaling factor. We note that this issue likely remained unnoticed
because \citet{DBLP:conf/ecai/BartKLM16} did not attempt to compute numerical
answers in their experiments.

@@

\paragraph{Instances.} For experimental data, we use the Bayesian networks
available with \textsf{Ace} and \textsf{Cachet}, most of which happen to be
binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
\item Mastermind, and
\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \citep{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
  \citep{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}
We run \textsf{ADDMC} with each of the five encodings once on each Bayesian
network.

%Specifically, \texttt{cw} solves the same number of
%instances in \SI{8.144}{\second} as \texttt{d02} does in \SI{1000}{\second},
%which is the second-best encoding in our experiments.

% TODO: need to update
\paragraph{Results.} \Cref{fig:cumulative} shows that \texttt{cd05} and
\texttt{cd06} (when run with \textsf{Ace}) are in the lead, while \textsf{ADDMC}
significantly underperforms when combined with any of the previous encodings.
Our encoding \texttt{cw} significantly improves the performance of
\textsf{ADDMC}, making $\textsf{ADDMC}+\texttt{cw}$ comparable to
$\textsf{Ace}+\texttt{d02}$, $\textsf{c2d}+\texttt{bklm16}$, and
$\textsf{Cachet}+\texttt{sbk05}$. Furthermore,
\cref{tbl:tallies} shows that, while $\textsf{Ace}+\texttt{cd06}$ managed to
solve the most instances, $\textsf{ADDMC}+\texttt{cw}$ was the best-performing
algorithm-encoding combination on the largest number of instances. The scatter
plot on the left hand side of \cref{fig:scatter} add to this by showing that
\texttt{cw} is particularly promising on Grid networks and tackles all DQMR
instances in less than a second. The scatter plot on the right hand side of
\cref{fig:scatter} shows that \texttt{cw} is better than \texttt{sbk05} (i.e.,
the second best performing encoding for \textsf{ADDMC}) on the majority of
instances. Seeing how, e.g., DQMR instances are trivial for
$\textsf{ADDMC}+\texttt{cw}$ but hard for $\textsf{Ace}+\texttt{cd06}$, and
vice versa for Mastermind instances, we conclude that the best-performing
algorithm-encoding combination depends significantly on (as-of-yet unknown)
properties of the Bayesian networks.

@@

We attempt to explain what makes \textsf{ADDMC} run hundreds of times faster
with \texttt{cw} than with any other encoding by considering asymptotic upper
bounds on the numbers of variables and ADDs based on the size and structure of
the Bayesian network. Let $n = |\mathcal{V}|$ be the number of vertices in the
Bayesian network, $d = \max_{X \in \mathcal{V}} |\mathrm{pa}(X)|$ the maximum
in-degree (i.e., the number of parents), and $v = \max_{X \in \mathcal{V}} |\im
X|$ the maximum number of values per variable. \Cref{tbl:asymptotes} shows how
\texttt{cw} has fewer variables and fewer ADDs than any other encoding. We
conjecture that it is primarily the reduced number of variables that makes the
\textsf{ADDMC} variable ordering heuristics much more effective. Note that these
are upper bounds and most encodings (including \texttt{cw}) can be smaller in
certain situations (e.g., with binary random variables or when a CPT has
repeating probabilities). We equate clauses and ADDs (more specifically, factors
of the function $\phi$ from \cref{alg:encoding}) here because \textsf{ADDMC}
interprets each clause of any WMC encoding as a multiplicative factor of the ADD
that represents the entire WMC instance \citep{DBLP:conf/aaai/DudekPV20}. For
literal-weight encodings, each weight is also a factor, but that does not affect
the asymptotic bounds in the table.

@@

% TODO: potential appendix: exact arguments to each piece of software
\end{document}
